---
title: "Untitled"
output: 
  revealjs::revealjs_presentation:
    self_contained: true
    incremental: true
    theme: simple
    highlight: pygments
    center: true
    transition: concave
    background_transition: fade
    reveal_options:
      slideNumber: false
      previewLinks: true
---


# Horizontal Slide 1

## Vertical Slide 1

## Vertical Slide 2

# Horizontal Slide 2

## {data-background-iframe="https://example.com"}

## {data-background-iframe="https://www.youtube.com/embed/nXY6PxAaOk0"}


## {data-background-video="kmeans_sim.mp4"}
## R Markdown

the importance of snippets
headers
library vs required
steps
folder strucutre


This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

